%%================================================
%% START Project info
%%================================================

%% Thesis for Master or Dissertation for PhD
\newcommand{\thesistype}{Thesis}

%% Thesis title in mixed case
\newcommand{\titleThai}{การพัฒนาระบบต้นแบบของสภาพแวดล้อมอัจฉริยะสำหรับผู้ใช้เก้าอี้รถเข็น}
\newcommand{\titleEng}{Prototyping Development of Smart Environment for Wheelchair User}
%% Line breaks for title pages only (do not use inside tabular rows)
\newcommand{\titleThaiCover}{การพัฒนาระบบต้นแบบของสภาพแวดล้อมอัจฉริยะ\\สำหรับผู้ใช้เก้าอี้รถเข็น}
\newcommand{\titleEngCover}{Prototyping Development of Smart Environment\\for Wheelchair User}

%% Student name(s) i.e. author(s) of this thesis
%% Order suggestion: by alphabetical order
\newcommand{\authorAThai}{นายวรพล แสงสระศรี}
\newcommand{\authorBThai}{นายศุภวิชญ์ อัศวลายทอง}
\newcommand{\authorAEng}{Mr. Worapon Saengsrasri}
\newcommand{\authorBEng}{Mr. Supawit Asawlaithong}


%% Degree that this thesis is for
\newcommand{\degreeThai}{วิศวกรรมศาสตรบัณฑิต}
\newcommand{\degreeEng}{Bachelor of Engineering}

%% Major
\newcommand{\majorThai}{วิศวกรรมไฟฟ้าและคอมพิวเตอร์}
\newcommand{\majorEng}{Electrical and Computer Engineering}

%% Date of submission
\newcommand{\submissionDayThai}{1}
\newcommand{\submissionDayEng}{1}
\newcommand{\submissionMonthThai}{พฤษภาคม}
\newcommand{\submissionMonthEng}{May}
\newcommand{\submissionYearThai}{2568}
\newcommand{\submissionYearEng}{2025}

%% Academic year for thesis submission
\newcommand{\academicYearThai}{2568}
\newcommand{\academicYearEng}{2025}

%% Institute/department
\newcommand{\facultyThai}{คณะวิศวกรรมศาสตร์}
\newcommand{\facultyEng}{Faculty of Engineering}

%% keywords
\newcommand{\keywordThai}{สภาพแวดล้อมอัจฉริยะ, ผู้ใช้เก้าอี้รถเข็น, บลูทูธพลังงานต่ำ, ระบบระบุตำแหน่งในอาคาร, อินเทอร์เน็ตของสรรพสิ่ง}
\newcommand{\keywordEng}{Smart environment, wheelchair user, Bluetooth Low Energy, indoor positioning, Internet of Things}

\newcommand{\headOfDepartmentThai}{ผู้ช่วยศาสตราจารย์ ดร. ศุภชัย วรพจน์พิศุทธิ์}
\newcommand{\headOfDepartmentEng}{Asst. Prof. Dr. Supachai Worapotphisut}
\newcommand{\advisorThai}{ผู้ช่วยศาสตราจารย์ ดร. ศุภชัย วรพจน์พิศุทธิ์}
\newcommand{\advisorEng}{Asst. Prof. Dr. Supachai Worapotphisut}

\newcommand{\committeeA}{กำหนดภายหลัง}
\newcommand{\committeeB}{กำหนดภายหลัง}
%\newcommand\dean{รองศาสตราจารย์ ดร. ธีร์ เจียศิริพงษ์กุล}
%%================================================
%% END Project info
%%================================================
