%%================================================
%% Abstract - English
%%================================================

This project presents the development of WheelSense, a prototype smart environment for wheelchair users in elderly care facilities. The system integrates motion sensing, indoor positioning, operational management, and caregiver decision support into an end-to-end data pipeline under deployable and maintainable infrastructure. The primary objective is to address safety limitations, cross-shift communication gaps, and paper-based data recording practices prevalent in Thai nursing homes.

The system architecture consists of four coordinated layers: (1) field device layer for motion detection and basic vital sign sensing; (2) indoor node layer for BLE beacon scanning and contextual enhancement; (3) edge server layer of the care facility for data ingestion, storage, and service delivery through authenticated interface sets; and (4) user interface layer covering role-based web dashboard and mobile applications. Indoor positioning employs RSSI fingerprinting with BLE beacons, utilizing the K-Nearest Neighbors (KNN) algorithm for zone and room-level inference on the server. An on-device AI assistant is integrated via machine-to-machine context protocol under a propose-confirm-execute workflow to ensure state-changing actions require prior confirmation and maintain resident data privacy within the care facility.

System prototype evaluation was conducted at Thammasat University covering four dimensions: (1) positioning robustness from field dataset~\cite{Sangsasri2026BLEMotionLLM}; (2) continuity and latency of the end-to-end data pipeline; (3) tool selection consistency and AI assistant latency from template-based test scenarios; and (4) role-based user experience from online questionnaires. Additionally, the project presented the prototype to administrators and caregivers of Vasanthawet Elderly Home to collect practical usage feedback without system installation at the facility.

Development results demonstrate the feasibility of integrating multi-layer technologies into a unified pipeline under cost, installation complexity, and data privacy constraints. Future work includes timestamp alignment across subsystems, expanding test cases to reflect real-world conditions, and improving user experience for caregivers in diverse contexts. These approaches are critical for deploying the system in residences, hospitals, and elderly care facilities in Thailand.
